Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-13 paper/paper.tex
reorganize paragraphs for ablation study

\subsection*{Is the dataset large enough for evaluation?}

@@

\subsection*{How important is feature extraction vs. metric learning?}

\section*{Analysis}

% TODO VL: clearly define a second part of the analysis from here onwards.
% we test the validity of the ablation study itself.
% we bring up alternate hypotheses and refute them one by one.
% like i did in ISMIR 2016.
In order to better understand the benefits of each design choice, an ablation study is now performed using a slightly different protocol.
In order to reduce the risk of misleading performance results using learning systems due to overfitting, we identify factors of variability that could lead to such problems and mitigate those.
\ja{Is this part of the ablation study or is this a ``meta'' consideration?}
In our case, two factors can readily be identified, the variability of the audio data and that of the perceptual judgments.

%\ja{We can expect better performance by using larger folds for the training %(i.e., not restricting ourselves to 2-fold cross validation).}
% VL: hors sujet.

>>>>

\subsection*{Is the dataset large enough for evaluation? Is the system overfitting?}

@@
